\begingroup
\renewcommand{\section}[2]{\anonsection{Перелік посилань}}
\begin{thebibliography}{00}

  \bibitem{ddd-evans}
      Evans E.
      Domain-Driven Design: Tackling Complexity in the Heart of Software,
      2003. 320 c. ISBN 9780321125217.

  \bibitem{ddd-article}
      Domain Driven Design -
      URL: https://martinfowler.com/bliki/
      DomainDrivenDesign.html
      (дата звернення 05.05.2021).

  \bibitem{agile-book}
      Meyer Bertrand.
      Agile! The Good, the Hype and the Ugly -
      URL: http://ndl.ethernet.edu.et/bitstream/123456789/67154/1/149\%20\%282\%29.pdf
      (дата звернення 05.05.2021).

  \bibitem{scrum-guide}
      Швабер, К. Сазерленд Д.
      Руководство по скраму. Исчерпывающее руководство по скраму: правила игры. -
      URL: https://brainrain.com.ua/scrum-guide/
      (дата звернення 05.05.2021).

  \bibitem{os-development}
      Пилон Д.
      Управление разработкой ПО. СпБ. : Издательство «Питер»,
      2018. 464 с. ISBN 978-5-459-00522-6.

  \bibitem{scrum-book}
      Рубин Кеннет С.
      Основы Scrum: практическое руководство по гибкой разработке ПО. М.: ООО «И.Д.Вильямс»,
      2016. 544 с. 
      % ISBN 978-5-8459-2052-2.

  \bibitem{thesis}
      Московко С.Г., Богач І.В.
      Аналіз архітектурних шаблонів програмного забезпечення.
			\emph{L Науково-технічна конференція факультету комп'ютерних систем і автоматики} :
			матеріали конференції ВНТУ, електронні наукові видання (м. Вінниця, 2021).
      - URL: https://conferences.vntu.edu.ua/index.php/all-fksa/all-fksa-2021/paper/view/11903/10500
			(дата звернення 0.5.05.2021).

	\bibitem{tdd-bdd-article}
			How to build quality software solutions using TDD and BDD? -
			URL: https://y-sbm.com/blog/difference-between-tdd-and-bdd
			(дата звернення 0.5.05.2021).

  \bibitem{business-rybakov}
      Рыбаков М.Ю.
      Бизнес-процессы: как их описать, отладить и внедрить. Практикум.
      Издательство Михаила Рыбникова, 2016. 392 с.

	\bibitem{tdd-article}
			What is Test Driven Development (TDD)? -
      URL: https://www.guru99.com/test-driven-development.html
			(дата звернення 0.5.05.2021).

	\bibitem{tdd-thesis}
			Khanam Z.
			Evaluating the Effectiveness of Test Driven Development: Advantages and Pitfalls.
      \emph{International Journal of Applied Engineering Research},
      2017. С. 7705–7716.
	
	\bibitem{bdd-article}
			Behavior Driven Development (BDD) -
			URL: https://www.agilealliance.org/glossary/bdd/
			(дата звернення 0.5.05.2021).

	\bibitem{bdd-article-2}
			Behavior Driven Development: Alternative to the Waterfall Approach -
			URL: https://www.agilest.org/devops/behavior-driven-development/
			(дата звернення 0.5.05.2021).
	
	\bibitem{ci-book}
			Duvall P.M. 
			Continuous Integration: Improving Software Quality and Reducing Risk,
			2007. 336 с. ISBN 9780321336385.
	
	\bibitem{ci-article}
			Continuous Integration -
			URL: https://www.agilest.org/devops/continuous-integration/
			(дата звернення 0.5.05.2021).
	
	\bibitem{de-article}
			How to publish and handle Domain Events -
			URL: http://www.kamilgrzybek.com/design/how-to-publish-and-handle-domain-events/
			(дата звернення 0.5.05.2021).

	\bibitem{solid-martin}
			Martin R.
			Clean Architecture: A Craftsman's Guide to Software Structure and Design,
			2017. 432 c. ISBN 9780134494166.
	
	\bibitem{ddd-pros-cons}
			What is Domain-Driven Design (DDD) | Pros \& Cons -
			URL: https://codezup.com/what-is-domain-driven-design-ddd-pros-cons/
			(дата звернення 0.5.05.2021).
	
	\bibitem{multitier-thesis}
			Кислач А.А.
			Многоуровневая архитектура,
			Мінск: БНТУ, 2016. С. 102–103.
	
	\bibitem{business-def}
			Business Logic Definition -
			URL: http://wiki.c2.com/?
      BusinessLogicDefinition (дата звернення 0.5.05.2021).
	
	\bibitem{user-story-article}
			User Stories with Examples and Template -
			URL: https://www.atlassian.com/agile/project-management/user-stories
			(дата звернення 0.5.05.2021).

  \bibitem{testig-black}
      Блэк Р. -
      Ключевые процессы тестирования.
      Планирование, подготовка, проведение, совершенствование. М. :Лори,
      2011. 544 с. ISBN 5-85582-239-7.

  \bibitem{test-automation-article}
      Инструменты автоматизации тестирования -
      URL: http://ru.qatestlab.com/technologies/software-infrastructure/test-automation-tools/
      (дата звернення: 05.05.2021).

  \bibitem{iso-software-eng}
      ISO/IEC 9126. 2001. Software engineering. -
      Software product quality. -
      Part 1: Qaulity model. 
      Part 2: External metrics. 
      Part 3: Internal metrics. 
      Part 4: Quality In use metrics -
      Geneva, Switzerland: International Organization for Standartization.

  \bibitem{rest-test}
      Автоматизация тестирования REST API при помощи Postman и JavaScript -
      URL: http://quality-lab.ru/test-automation-rest-api-using-postman-and-javascript/
      (дата звернення: 05.05.2021).

  \bibitem{rest-test-asanov}
      Асанов П.
      Автоматизация функционального тестирования REST API:
      секреты, тонкости и подводные камни -
      URL: https://sqadays.com/ru/talk/34635
      (дата звернення: 05.05.2021).

\end{thebibliography}
\endgroup

\clearpage
